Test of Adaptable User Interfaces

### 2015-07-08 paper.tex

% =============================================================================
\section{Case Study}
The case study used in this work is a prototype for a smart home energy management system. This decision is based on the fact that it is a modern concept, little explored in the domain of this research and whose UIs can be adapted to several contexts. A smart home may be defined as a well-designed structure with sufficient access to assets, communication, controls, data, and information technologies for enhancing the occupants' quality of life through comfort, convenience, reduced costs and increased connectivity~\cite{smart-home-harper}. A smart home energy management system is an energy management system applied to smart homes. It allows users to control and monitor the energy consumption in a residence from different devices.

@@

% =============================================================================
\section{Conclusions and Perspectives}
% =============================================================================
TODO

>>>>

% =============================================================================
\section{Case Study}
% =============================================================================

\marginpar{
\begin{figure}
  \begin{center}
  \includegraphics[width=\marginparwidth]{images/web0_goal-filter.eps}
  \caption{Une figure dans la marge.}
  \label{fig:marginparsample}
  \end{center}  
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=\marginparwidth]{images/mobile_goal-filter.eps}
  \caption{Une figure dans la marge.}
  \label{fig:marginparsample}
  \end{center}  
\end{figure}
}

The case study used in this work is a prototype for a smart home energy management system. This decision is based on the fact that it is a modern concept, little explored in the domain of this research and whose UIs can be adapted to several contexts. A smart home may be defined as a well-designed structure with sufficient access to assets, communication, controls, data, and information technologies for enhancing the occupants' quality of life through comfort, convenience, reduced costs and increased connectivity~\cite{smart-home-harper}. A smart home energy management system is an energy management system applied to smart homes. It allows users to control and monitor the energy consumption in a residence from different devices.

@@

% =============================================================================
\section{Conclusions and Perspectives}
% =============================================================================
Because of the similarities, these scripts could easily be generated from a single script, containing the abstract test cases and the implementation details. Tobias could do it if its entry language syntax (TSLT) would be improved.
TODO
